\clearpage
\thispagestyle{plain}

\begin{center}
  \textbf{Acknowlegments}
\end{center}

I would like to thank my advisor Andrew Jordan for his constant help and guidance throughout my graduate studies.  Beyond his aid in my growth as a scientist, I also owe him an enormous debt of gratitude for allowing me to join and work in his group during a period when I needed many special acommodations due to a long term illness.  Without his help, it is likely I would have been unable to finish work on my Master's degree, much less complete my doctoral studies.

I have been very fortunate to collaborate with a number of highly talented physicists in my work.  Fellow group members Justin Dressel and Shengshi Pang both made projects I was a part of much stronger than they otherwise would have been, and both have introduced me to physical and mathematical concepts I otherwise would not have known about.  I must also thank Justin Dressel in particular for spending a large amount of time and effort helping me get up to speed in my first research efforts in the group.  I have also had the opportunity to work with John Howell and Paul Kwiat on several papers and would like to thank both for their ideas, insights, and contributions.

Laura Blumkin has helped me with every possible administrative item since she joined the department, and has consistently made my life much easier.  I am particularly grateful for the assitance related to navigating my graduate studies while dealing with my illness.

Finally, I cannot thank my family enough for their help during my degree work. Even with the arrival of two daughters, I have had the luxury of focusing on physics with very little interruption.  This would not have been possible without their help, and is especially due to the extraordinary efforts of my wife Dana. 

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
